### 2012-06-06 notes/coop.tex
Added a new file

\documentclass{article}
\usepackage{array}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{times}

@@

>>>>

\documentclass{article}

@@

\hline

A set of tasks needs to be performed,
\begin{itemize}
	\item they require different expertises
	\item they may be decomposed.
\end{itemize}

Agents do not have enough resource on their own to perform a task.

Find complementary agents to perform the tasks
\begin{itemize}
	\item robots have the ability to move objects in a plant, but multiple robots are required to move a heavy box.
	\item transportation domain: agents are trucks, trains, airplanes, ships... a task is a good to be transported.
\end{itemize}

Issues:
\begin{itemize}
	\item What coalition to form?
	\item How to reward each each member when a task is completed?
\end{itemize}

\hline
